### 2017-01-17 paper/evaluation.tex
Updated plots from RQ2
adjusting plots (per request)

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  However, use of parallelism
does not assure speedups on those projects.  We analyzed one sensible
factor that is critical to the effectiveness of parallelism: the
amount of tests that dominate execution time.  In the limit, if cost
is dominated by a single test, it is unlikely that parallelization
will be beneficial as a test method is the smallest working unit in
test frameworks (see Section~\ref{sec:frameworks}).

@@

We evaluated the dispersion of time distributions (one distribution
per project) to answer research question \numRQB{}.  To measure
dispersion \emph{across} projects we used Relative Standard Deviation
(RSD)~\cite{everitt-book-stats-2010}.  Note that, if we were to
analyze each project in isolation, the standard deviation of a
distribution ($\sigma$) would suffice to quantify how dispersed the
(time) distribution is.  However, in our case, we would like to be
able to compare and summarize dispersion across projects.  The RSD,
which is obtained dividing the standard deviation by the mean ($\mu$)
of a distribution, provides such normalization effect.  This metric
provides a lower bound (zero) but not an upper bound (somewhere close
to 1).  The smaller (larger) the value of RSD the more (less) uniform
the distribution is.  Consequently, ignoring other factors that affect
performance of parallelization (e.g., CPU/IO ratio), the lower the
value of RSD the more parallelizable a test suite should be.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{R/testcost.pdf}  
  \caption{\label{fig:relativesd}Distribution of RSD ($\sigma/\mu$)
    across projects.}
\end{figure}

Figure~\ref{fig:relativesd} shows the distribution of RSD across
medium and long-running projects.  Results show that the distribution
is skewed to the right indicating that test costs are relatively well
distributed in most costly projects we analyzed \Fix{$\leftarrow$
  confirm}.

>>>>

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  However, parallelism by itself does
not assure speedups on those projects.  One sensible factor that is
critical to the effectiveness of parallelism is the distribution of
test costs in the test suite.  In the limit, if cost is dominated by a
single test, it is unlikely that parallelization will be beneficial as
a test method is the smallest working unit in test frameworks (see
Section~\ref{sec:frameworks}).

\Fix{...elaborate...}

@@

%% We also evaluated the dispersion of time distributions (one
%% distribution per project) to answer research question \numRQB{}.  To
%% measure dispersion \emph{across} projects we used Relative Standard
%% Deviation (RSD)~\cite{everitt-book-stats-2010}.  Note that, if we were
%% to analyze each project in isolation, the standard deviation of a
%% distribution ($\sigma$) would suffice to quantify how dispersed the
%% (time) distribution is.  However, in our case, we would like to be
%% able to compare and summarize dispersion across projects.  The RSD,
%% which is obtained dividing the standard deviation by the mean ($\mu$)
%% of a distribution, provides such normalization effect.  This metric
%% provides a lower bound (zero) but not an upper bound (somewhere close
%% to 1).  The smaller (larger) the value of RSD the more (less) uniform
%% the distribution is.  Consequently, the lower the value of RSD the
%% more parallelizable a test suite should be.

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{R/testcost-med.pdf}
        \caption{\label{fig:medtcost}}
    \end{subfigure}\\
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{R/testcost-long.pdf}
        \caption{\label{fig:longtcost}}
    \end{subfigure}%
    \caption{\label{fig:relativesd}Distribution of RSD ($\sigma/\mu$)
        across projects.}
\end{figure}

%% \begin{figure}[h!]
%%   \centering
%%   \includegraphics[width=0.5\textwidth]{R/testcost.pdf}  
%%   \caption{\label{fig:relativesd}Distribution of RSD ($\sigma/\mu$)
%%     across projects.}
%% \end{figure}

%% Figure~\ref{fig:relativesd} shows the distribution of RSD across
%% medium and long-running projects.  Results show that the distribution
%% is skewed to the right indicating that test costs are relatively well
%% distributed in most costly projects we analyzed \Fix{$\leftarrow$
%%   confirm}.
